---
output: github_document
---
<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![CRAN status](https://www.r-pkg.org/badges/version/ibmsunburst)](https://CRAN.R-project.org/package=ibmsunburst)
[![Codecov test
coverage](https://codecov.io/gh/jumpingrivers/ibmsunburst/branch/main/graph/badge.svg)](https://app.codecov.io/gh/jumpingrivers/ibmsunburst?branch=main)
[![R-CMD-check](https://github.com/jumpingrivers/ibmsunburst/workflows/R-CMD-check/badge.svg)](https://github.com/jumpingrivers/ibmsunburst/actions)
<!-- badges: end -->


```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
 fig.path = "man/figures/"
)
```

# IBM Personality Insights sunburst diagrams in R

The goal of {ibmsunburst} is to wrap the [JavaScript library that IBM have produced](https://github.com/personality-insights/sunburst-chart/) for making sunburst personality insights charts for use in R and R Markdown documents.

Work on this package was part-sponsored by [Hendrik Feddersen](//github.com/Hendrik147), a prominent HR Analytics advocate.

## Installations

Install {ibmsunburst} from GitHub

```r
# install.packages("remotes")
remotes::install_gitub("jumpingrivers/imbsunburst")
```

## Example

Below we input the path to a JSON file corresponding to the output of [IBM Watson Personality Insights service](https://www.ibm.com/watson/services/personality-insights/) and visualize it.

```{r sunburst}
json_path <- system.file(
  "extdata", "profiles",
  "en_v2.json", package = "ibmsunburst"
)

ibmsunburst::ibmsunburst(json = json_path, version = "v2")

```

You can use the function on a list, on JSON or on a filepath, making it quite handy for integration in your workflow. 

There is no R wrapper for the [IBM Personality Insight API](https://www.ibm.com/watson/developercloud/personality-insights/api/v3/) itself yet, but you could use it with {httr}, as shown in a very short example in the vignette.

## Dev notes

[Kent Russell](https://github.com/timelyportfolio) added some documentation of the changes that he made to the source [sunburst-chart](https://github.com/personality-insights/sunburst-chart) JavaScript library. Find them [here](inst/dev_notes.md).

## Code of Conduct
  
Please note that the ibmsunburst project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.

